### 2019-07-07 manuscript.Rmd
manuscript

Although these tools provide various approaches to perform SA, they each individually have limitations for application to pharmacokinetic and PK modeling. We present here an \proglang{R} package, called \pkg{pksensi}, which is designed to make SA more accessible and reproducible in pharmacological and toxicological researches. This package can investigate both parameter uncertainty and sensitivity in pharmacokinetic and PK model with multivariate model outputs. Moreover, it seamlessly integrates with both general ODE solvers available in R or as external \proglang{C} code, as well as the \pkg{GNU MCSim} software used for conducting sophisticated PK modeling, including MCMC. The analytical framework in \pkg{pksensi} not only include global SA but the uncertainty analysis and diagnostic tool to support the modeling process. The design concepts of \pkg{pksensi} are:

>>>>

Although these tools provide various approaches to perform SA, they each individually have limitations for application to pharmacokinetic and PK modeling. For example, the estimated index in SA is not robust when using the inadequate size of the sample number. However, there are no software packages that provide the available tools in the assessment of reliability. In addition, the developed eFAST function doesn't include the feature to generate the random sampling curve. We present here an \proglang{R} package, called \pkg{pksensi}, which is designed to make SA more accessible and reproducible in pharmacological and toxicological researches. This package can investigate both parameter uncertainty and sensitivity in pharmacokinetic and PK model with multivariate model outputs. Moreover, it seamlessly integrates with both general ODE solvers available in R or as external \proglang{C} code, as well as the \pkg{GNU MCSim} software used for conducting sophisticated PK modeling, including MCMC. The analytical framework in \pkg{pksensi} not only include global SA but the uncertainty analysis and diagnostic tool to support the modeling process. The design concepts of \pkg{pksensi} are:
